The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190917v1.tex
CIV tex/ tidy up

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nunc imperdiet facilisis volutpat. Phasellus ultricies justo a ante bibendum porta. Nulla varius convallis risus in tincidunt. Vivamus sit amet massa non dui volutpat porttitor. Donec imperdiet mauris non risus commodo tempor. Nulla volutpat nulla a lorem lobortis, a luctus nulla rhoncus. Vestibulum vel ante elementum nisl feugiat sollicitudin. Aenean purus sem, mattis vitae odio et, varius vehicula nulla.
%%
Nulla ante mauris, mattis a tristique eu, pharetra eget erat. Cras et ultrices lectus. Praesent augue erat, commodo ac malesuada vel, mattis ac nisi. Quisque eu vehicula urna, in fringilla nunc. Duis faucibus scelerisque felis, sollicitudin luctus tortor pretium dapibus. Sed cursus scelerisque dapibus. Proin a bibendum neque, sit amet aliquet arcu. Vivamus in eros lectus. Nam dui felis, convallis sit amet dolor ut, dignissim posuere nunc. Donec egestas tellus vel urna interdum tincidunt. Sed orci eros, convallis in rhoncus sit amet, tincidunt ac est. Mauris tempus, diam a euismod tempus, est turpis laoreet justo, quis posuere augue ipsum sed nisi. Aliquam non lobortis tellus. Morbi vulputate porta placerat. Quisque dapibus pretium arcu eget tempor. Aenean in tincidunt nisi. Aenean interdum congue enim.
\end{abstract}

@@

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
\citep[e.g][]{NodaDone2018, Ruan2019}.

While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
%% 
Here, we report on three objects 
SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in the \civ broad emission line
properties, as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift and for emission lines with high ionization potentials
(I.P.'s $>$13.6 eV).

@@

\subsection{Literature Search}
\citet{Wilhite2006} examine the variability of the high-ionizaton
C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
correlation between the change in the C~\textsc{iv} line flux and the
change in the line width, but no correlations between the change in
flux and changes in line center and skewness.  The relation between
line flux change and line width change is consistent with a model in
which a broad line base varies with greater amplitude than the line
core. The objects studied here are more luminous and at higher
redshift than those normally studied for variability, ranging in
redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
roughly $-$24 to $-$28.  Using moment analysis line-fitting
techniques, we measure line fluxes, centers, widths and skewnesses for
the C~\textsc{iv} line at two epochs for each object.  The well-known
Baldwin Effect is seen for these objects, with a slope $\beta =
-0.22$.  The sample has a median intrinsic Baldwin Effect slope of
$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  Additionally, we find
no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
indicating that this blueshift might be useful as a measure of
orientation.

@@

Denney, Klly; SDSS-RM Team \\
The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project\\
http://adsabs.harvard.edu/abs/2015AAS...22520403D\\

@@

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
\subsection{Selection/Identification}

\subsection{SDSS spectra}
\begin{table}
 \centering
 \begin{tabular}{l l l l}
  \hline \hline 
% &&\\
   Quantity \ Object                           & J2228+2201     &  J1638+2827 \\
% &&\\
 \hline 
    &&\\
    R.A. / deg                                        &    337.078194      &  249.720559\\
    Declination / deg                            &    +22.017478      &  +28.452159 \\
    redshift, $z$                                    &   2.222$\pm$0.00038   &  2.185$\pm$0.00043          \\
    &&\\ 
    \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
 %   &&\\ 
    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
    &&\\
    \hline \hline 
  \end{tabular}
  \caption{Physical properties of J1100-0053, J2317+0005 and J1052+1519 using the
    methods from \citet{Shen2011}. *This spectrum was used to estimate
    the quantities reported.  We use the regular definition of $L_{\rm
      Edd} = 4 \pi G M m_{\rm p} c /\sigma_{T} =
    1.26\times10^{38}\left (M/M_{\odot} \right )$ erg s$^{-1}$.} 
 \label{tab:Shen_props}
\end{table}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{In the context of CLQs at lower-$z$}

\subsection{Balmer CLQs vs. \civ CLQs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}

>>>>

\begin{abstract}
This is two hundred words, the suggested maximum for a MNRAS
Letter. Lorem ipsum dolor sit amet, autem semper eam ei. Eros
maluisset posidonium eu mea, atqui aperiam nostrum cum ad. Te vocent
volutpat petentium vix, pro senserit convenire vituperatoribus ex, ad
his mucius tamquam appetere. An mea omnium voluptaria scribentur, te
verear iisque vulputate sit. Vim malis omittam probatus cu, vide
tempor ius ex, vim eu case magna rebum. Vis id clita eruditi, in sea
evertitur dissentiunt, per eu deseruisse mnesarchum deterruisset. Eu
tale tempor sea, te mundi congue detracto est. Has ipsum animal timeam
no. Atqui novum nobis et his, pericula interesset mel ut. Ea pro eros
everti legendos. Vel iusto legere euismod id, ea erat debitis
democritum usu. Ut paulo aliquid vix, disputationi delicatissimi
signiferumque ut eam. Utroque impedit ad his. Ei mea sale tritani, ex
eum duis epicuri, at per nonumy delectus electram. Dolorem patrioque
prodesset vis at, sint tritani mel te. Ut nulla solet nonumes has, mel
diam scripta delectus in, ne duo laudem appetere assueverit. An vim
reque munere, labores apeirian his cu. Ei clita placerat praesent nam,
in affert sapientem est. Qui te regione deterruisset. Nam at quodsi
placerat. Pri no quando placerat.
\end{abstract}

@@

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
\citep[e.g][]{NodaDone2018, Ruan2019}. 
%
These CLQs have primarily been defined according to their Balmer emission line properties with 
particular attention paid to the H$\beta$ emission line, usually observed from optical spectroscopy. 
As such, current CLQ studies have been at redshifts $z<1$.

While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
%%

I also don’t think this is a recombination (for H, He) vs. collisionally excited lines (MgII, C IV etc.) thing, though I’m not sure.

Here, we report on three objects 
SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in the \civ broad emission line
properties, as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift and for emission lines with high ionization potentials
(I.P.'s $>$13.6 eV).

@@

In this paper we use the wavelengths of 1548.2 and 1550.8 \AA for the \civ doublet
%Example of how to reference these results:
using the values from the National Institute of Standards and Technology (NIST) Atomic Spectra Database 
\citep{Kramida2018}. 
% A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018). NIST Atomic Spectra Database (ver. 5.6.1), [Online]. Available: https://physics.nist.gov/asd [2019, September 17]. National Institute of Standards and Technology, Gaithersburg, MD. DOI: https://doi.org/10.18434/T4W30F

%The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
%11.3 eV is the energy needed for C I to get rid of one electron, and become singly-ionised C II”
%“24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
for ionisation energies, we note 47.89 eV  (3.519 Ry) is the energy required to for neutral C to dislodge three electrons and become triply--ionised \civ, 
and where 64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.

\subsection{Literature Search}
\citet{Gregory1982} reported time variability in both Lya and \civ 1550 emission lines in the Seyfert galaxy NGC 5548.

From \citet{VandenBerk2001} 
The rest positions of emission lines in quasar spectra, especially the
high-ionization broad lines, are known to vary from their nominal
laboratory wavelengths \citep{Gaskell1982, Wilkes1986,  Espey1989, Espey1990Erratum, 
ZhengSulentic1990, Corbin1990, Weymann1991, TytlerFan1992, 
Brotherton1994, Laor1995, McIntosh1999}.

\citet{Wilhite2006} examine the variability of the high-ionizaton
C~\textsc{iv}$\lambda{1549}$ line in a sample of 105 quasars observed
at multiple epochs by the Sloan Digital Sky Survey.  We find a strong
correlation between the change in the C~\textsc{iv} line flux and the
change in the line width, but no correlations between the change in
flux and changes in line center and skewness.  The relation between
line flux change and line width change is consistent with a model in
which a broad line base varies with greater amplitude than the line
core. The objects studied here are more luminous and at higher
redshift than those normally studied for variability, ranging in
redshift from 1.65 to 4.00 and in absolute $r$-band magnitude from
roughly $-$24 to $-$28.  Using moment analysis line-fitting
techniques, we measure line fluxes, centers, widths and skewnesses for
the C~\textsc{iv} line at two epochs for each object.  The well-known
Baldwin Effect is seen for these objects, with a slope $\beta =
-0.22$.  The sample has a median intrinsic Baldwin Effect slope of
$\beta_{int} = -0.85$; the C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  Additionally, we find
no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects,
indicating that this blueshift might be useful as a measure of
orientation.

@@

\citet{Denney2015}, 
%Denney, Kelly; SDSS-RM Team, ``The Effects of S/N on Measuring CIV Broad Emission Line Widths in Quasars - An Early Science Result from the Sloan Digital Sky Survey Reverberation Mapping Project'' ; http://adsabs.harvard.edu/abs/2015AAS...22520403D
The Sloan Digital Sky Survey Reverberation Mapping (SDSS-RM) Project
spectroscopically monitored $\sim$850 quasars over a seven square
degree field for approximately six months with the BOSS
spectrograph. While the time series analysis of the quasar continuum
and emission-line variability, and thereby the potential to measure
reverberation time delays from this sample, is still underway, we have
used the subset (roughly half) of this sample containing the \civ 1549\AA 
broad emission line to investigate the effects of S/N on measuring
this broad emission line width. Line width measurements are necessary
for inferring the broad line region gas velocities used to determine
the quasar black hole mass. However, literature studies have suggested
line width measurements, and therefore black hole mass estimates, may
be biased by the use of relatively low S/N, typical survey-quality,
data, compared to the high S/N data that calibrate single-epoch black
hole mass scaling relations. The SDSS-RM data set provides a unique
opportunity to search for any systematic uncertainties in CIV line
width measurements through a comparison of line widths measured from
the single-epoch spectra, which are roughly equivalent to other
SDSS/BOSS quasar spectra (though still twice the exposure time) to
those measured from the high-S/N, campaign co-added spectra, which
contain more than 30 epochs of each source. Here we present results
from this investigation, which have implications for estimating CIV
single-epoch black hole masses from the SDSS/BOSS and other surveys.

@@

\citet{Coatman2016} show that %%Black hole masses are crucial to understanding the physics of the connection between quasars and their host galaxies and measuring cosmic black hole-growth. 
at high redshift, $z>2.1$, black hole masses are normally derived using the velocity width of the C IV λλ1548, 1550 broad emission line, based on the assumption that the observed velocity widths arise from virial- induced motions. In many quasars, the C IV emission line exhibits significant blue asymmetries (‘blueshifts’) with the line centroid displaced by up to thousands of km s−1 to the blue. These blueshifts almost certainly signal the presence of strong outflows, most likely originating in a disc wind. We have obtained near-infrared spectra, including the Hα λ6565 emission line, for 19 luminous (LBol = 46.5–47.5 erg s−1) Sloan Digital Sky Survey quasars, at redshifts 2 < z < 2.7, with C IV emission lines spanning the full range of blueshifts present in the population. A strong correlation between C IV velocity width and blueshift is found and, at large blueshifts, >2000kms−1, the velocity widths appear to be dominated by non-virial motions. Black hole masses, based on the full width at half-maximum of the C IV emission line, can be overestimated by a factor of 5 at large blueshifts. A larger sample of quasar spectra with both C IV and H β, or Hα, emission lines will allow quantitative corrections to C IV-based black hole masses as a function of blueshift to be derived. We find that quasars with large C IV blueshifts possess high Eddington luminosity ratios and that the fraction of high-blueshift quasars in a flux-limited sample is enhanced by a factor of approximately 4 relative to a sample limited by black hole mass.

@@

Also from \citet{Richards2011}, 
At high redshift, two well-known properties of the Civ emission line are evident in quasar spectra (see Section 4). An anti-correlation between luminosity and the equivalent width (EQW) of C iv, generally known as the Baldwin Effect (BEff; Baldwin 1977), was first identified in 20 (mostly radio-loud (RL)) quasars and has been confirmed in much larger samples (e.g., Wu et al. 2009). The other effect is the blueshifting of the C iv with respect to the systemic redshift (Gaskell 1982; Wilkes 1984). As with the BEff, these blueshifts have not only been confirmed with larger samples, but appear to be nearly ubiquitous in the quasar population (Sulentic et al. 2000b; Richards et al. 2002a).

@@

\iffalse
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J2228+2201.png}
  \vspace{-12pt}
  \caption[]{J222818.7+220102.6. 
% EMERGING., 
The light curve shows it brightening from 20.5 to 19.5 over the 771 days observed-frame between the two SDSS spectra available. 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] emerging on a new blue contiuum slope.}
  \label{fig:disk_suppression}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/J1638+2827.png}
  \vspace{-12pt}
  \caption[]{The quasar SDSS J163852.9+282708. 
% Disappearing 
A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.}
  \label{fig:disk_suppression}
\end{figure}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
%\subsection{Selection/Identification}
%\subsection{SDSS spectra}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

\begin{table}
 \centering
 \begin{tabular}{l l l l}
  \hline \hline 
% &&\\
   Quantity \ Object                           & J2228+2201     &  J1638+2827 \\
% &&\\
 \hline 
    &&\\
    R.A. / deg                                        &    337.078194      &  249.720559\\
    Declination / deg                            &    +22.017478      &  +28.452159 \\
    redshift, $z$                                    &   2.222$\pm$0.00038   &  2.185$\pm$0.00043          \\
    &&\\ 
    \multirow{2}{*}{Plate, Fiber, MJD}   & 6118, 720, 56189	     &  2948, 614, 54553	  \\
                                         & 7582, 790, 56960	     & 5201, 178, 55832 \\    
 %   &&\\ 
    %$M_{i}(z=2)$  / mag                          &   ?                       & ?                \\
    %log $(L_{\rm bol} / {\rm erg s}^{-1}) $      &   ?             & 45.56$\pm$0.004      & 45.07$\pm$0.004 \\
    %log $(M_{\rm BH} / M_{\odot})  $           &  ?                  & 8.43$\pm$0.03           & 8.46$\pm$0.02 \\
    %Eddington ratio  (\%)                        &  ?                               &  10.7                           &  3.2     \\ 
    &&\\
    \hline \hline 
  \end{tabular}
  \caption{Physical properties of J1100-0053, J2317+0005 and J1052+1519 using the
    methods from \citet{Shen2011}. *This spectrum was used to estimate
    the quantities reported.  We use the regular definition of $L_{\rm
      Edd} = 4 \pi G M m_{\rm p} c /\sigma_{T} =
    1.26\times10^{38}\left (M/M_{\odot} \right )$ erg s$^{-1}$.} 
 \label{tab:Shen_props}
\end{table}

@@

%%\newpage
%% For the MNRAS Letter, not sure this can take up a full page...
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
% {figures/The_3_CIV_CLQs_20190917.pdf}
   \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
SDSS J1205+3422 (top), 
SDSS J1638+2827 (middle), 
SDSS J2228+2201 (bottom). 
%A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
}
  \label{fig:civ_clqs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
nulla. Nullam eu augue id purus mollis dignissim sed et
libero. Phasellus eget justo sed neque pellentesque egestas nec id
arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
neque id mi ultrices tristique. Integer quam libero, ornare vel
gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
cursus, dui nisl egestas augue, non fermentum nisl est nec
nisi. Vestibulum nec mi justo, eget dapibus velit.

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {../plots/Wilhite/Wilhite_2006_Fig2_redux_20190830.png}
% {figures/The_3_CIV_CLQs_20190917.pdf}
   \vspace{-12pt}
  \caption[]{
The Change in \civ line width vs. line flux change. 
Data from \citet{Wilhite2006} with a sample of 105 quasars observed at
multiple epochs by the Sloan Digital Sky Survey. We find a strong
correlation between the change in the C iv line flux and the change in
the line width, but no correlations between the change in flux and
changes in line center and skewness.}
  \label{fig:Wilhite2006_comparison}
\end{figure}
From Figure~\ref{fig:Wilhite2006_comparison} there appears to be a
strong correlation between the change in the line flux and the change
in the line width.  Figure~\ref{fig:Wilhite2006_comparison} shows the
epoch-to-epoch flux ratio versus the ratio of line widths.

In the context of CLQs at lower-$z$...  Sociis natoque penatibus et
magnis dis parturient montes, nascetur ridiculus mus. Duis tempus,
lectus nec ultricies mollis, mi orci feugiat nulla, a bibendum velit
orci nec lacus. Duis a odio in nisi egestas dictum. Nullam vel quam
mauris, eget consectetur orci. Morbi ac mi sit amet neque consectetur
tempus ac eget est. Curabitur malesuada arcu sit amet metus dictum at
dapibus arcu accumsan. Fusce sollicitudin luctus rutrum.  Balmer CLQs
vs. \civ CLQs...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
nulla. Nullam eu augue id purus mollis dignissim sed et
libero. Phasellus eget justo sed neque pellentesque egestas nec id
arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
neque id mi ultrices tristique. Integer quam libero, ornare vel
gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
cursus, dui nisl egestas augue, non fermentum nisl est nec
nisi. Vestibulum nec mi justo, eget dapibus velit.

Cras in laoreet mauris. Vivamus nec nulla a dui commodo
adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
sagittis quis in sem. Phasellus quis risus bibendum eros luctus
auctor.

Etiam mollis viverra nisi eget aliquet. Aliquam erat volutpat. Vivamus
tristique, nisl eu malesuada semper, libero tortor convallis elit, a
scelerisque orci nisi lacinia turpis. In lacinia ultrices
volutpat. Proin ultrices luctus tellus, in placerat eros tincidunt
id. Ut varius iaculis quam in consequat. Nulla nec orci est, sit amet
pellentesque nisl. Mauris non cursus lectus. Praesent placerat leo vel
erat gravida lacinia. Donec vehicula consectetur lectus vitae
luctus. Praesent nisl justo, laoreet elementum facilisis vel,
tristique ac enim. Etiam vel quam ut quam eleifend
tincidunt. Suspendisse sit amet eros vel elit ullamcorper
laoreet. Etiam venenatis sodales turpis, nec lacinia ligula hendrerit
nec. Nam eu vulputate purus. Quisque facilisis congue metus, sed
imperdiet lorem rhoncus sit amet.

In this paper we have... 
\begin{itemize}
\item Pellentesque vel elit neque, in interdum lacus. Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a; 
\item At sit amet sapien a risus dapibus sagittis. Cras sed ultricies erat. Donec id metus sed urna lacinia convallis vel sed enim. 
\item Nisi libero, ornare vel bibendum eu, sollicitudin sed leo. Cras tincidunt aliquet ultricies. Cras pretium velit leo, in malesuada. 
\item Duis sagittis ultricies interdum. Proin sit amet sem nec metus feugiat pharetra.
\end{itemize}

Aliquam ac metus nec odio tempus pharetra sed nec diam. Sed eget arcu
nulla. Etiam elementum ultrices ligula, at iaculis libero feugiat
bibendum. Suspendisse potenti. Nam pharetra adipiscing
euismod. Quisque imperdiet dignissim odio, sed volutpat justo
tincidunt eu. Nunc vehicula pharetra suscipit. Integer aliquet pretium
ipsum vel ultrices. Nam rutrum nibh ac quam pulvinar molestie.

Sed sed ipsum diam. In risus tortor, sagittis eu auctor in, varius in
dui. Mauris a nunc ut ligula ullamcorper tincidunt. Nunc aliquam eros
ac risus pellentesque aliquam. Phasellus augue velit, varius at
porttitor sit amet, pretium eget felis. Ut mollis tellus elementum
magna porttitor rutrum. Etiam blandit leo eget est consectetur
imperdiet. Quisque et diam nec orci vulputate varius vitae id sapien.
